### 2012-11-12 paper.tex
completed mapreduce

\subsubsection{Addons to the MapReduce library}

\subsection{Camdoop}
%Preprocessing instead of post processing

\subsection{Mantri}
% Load balancing tasks and reduce the effects caused by outliers

\subsection{Nectar}

\subsection{Optimising data shuffling in Data Parallel Computation}

>>>>

\subsubsection{Addons to the MapReduce library}
There has been some additions made to the MapReduce library on top of the basics as detailed above.\\

Firstly, the users of the library can not only define the number of \emph{map} and \emph{reduce} tasks, but also the way the output data is partitioned. This is especially useful in cases where the hierarchical string, and only a certain part of the string should be taken as the identifier when partitioning.\\

Another addon which may come in useful to most users is that the partition files are sorted in ascending order. This would allow future users of the file to easily look for the data they require within the file.

A useful addon to reduce network I/O would be the combiner. In essence the combiner just runs the \emph{reduce} function right after \emph{map}, and write it to the intermediate output file. For example, in a program that counts the total number of words there are might have plenty of duplicate words due to the map function. What the combiner  would do is to merge this data together first so that instead of sending thousands of records over, it can be sent as a few records.

\subsection{Addition enhancement to MapReduce}
%each of these sections should take around 1.5 to 2 pages.
\subsubsection{Camdoop}
%Preprocessing instead of post processing

\subsubsection{Mantri}
% Load balancing tasks and reduce the effects caused by outliers

\subsubsection{Nectar}

\subsubsection{Optimising data shuffling in Data Parallel Computation}
